### 2025-06-07 download-football-data.qmd
20250607 - fixes

nfl_standings_raw <- nflseedR::nfl_standings(nfl_schedules) #read_csv("http://www.habitatring.com/standings.csv"); archived at: https://perma.cc/5QLN-VK7V
```

@@

save(
  nfl_actualFantasyPoints_player_career,
  file = "./data/nfl_actualFantasyPoints_career_raw.RData"
)
```

>>>>

nfl_standings_raw <- nflseedR::nfl_standings(
  nfl_schedules%>% filter(!is.na(result))) #read_csv("http://www.habitatring.com/standings.csv"); archived at: https://perma.cc/5QLN-VK7V
```

@@

save(
  nfl_actualFantasyPoints_player_career_raw,
  file = "./data/nfl_actualFantasyPoints_career_raw.RData"
)
```
